\mytitle

### 2023-05-15 chapters/depsynth/synthesis.tex
Increase font size for depsynth algorithms

\begin{figure}
    \centering
    {\xsmall\input{figs/alg.tex}}
    \caption{The \depsynth algorithm takes as input a storage system implementation $\sys$,
    a set of litmus tests \tests, and a crash-consistency predicate $\textrm{\emph{Consistent}}$,
    and returns an acyclic set of dependency rules that make all tests in \tests crash consistent (\cref{def:crash-consistent}).
    The search synthesizes dependency rules for one litmus test at a time.
    If the rules generated for two or more tests result in a cycle,
    this algorithm fails; \cref{sec:alg:cycles} discusses an extension for continuing 
    the search for an acyclic solution.}
    \label{fig:alg:depsynth}
\end{figure}

@@

\begin{figure}
    \centering
    {\xsmall\input{figs/rules.tex}}
    \caption{The algorithm for generating sufficient dependency rules for a litmus test \test
    searches the space of happens-before graphs over the writes performed by \test.
    The first phase searches for total orders over the writes that are sufficient for crash consistency.
    Once such a total order is found, the second phase removes edges from it until the happens-before graph is minimal.}
    \label{fig:alg:rulesfortests}
\end{figure}

\begin{figure}
    \centering
    {\xsmall\input{figs/rulesforgraph.tex}}
    \caption{The procedure for generalizing a happens-before graph \gr into dependency rules
    constructs (at most) one rule for each edge.}
    \label{fig:alg:rulesforgraph}
\end{figure}

@@

\paragraph{Partial order search.}
Starting from a happens-before graph \gr that reflects a total order over all writes in \test,
\phasetwo (line~\ref{fig:rules:phase2})
removes edges from the graph until it is minimal,
i.e., removing any further edges would violate crash consistency.
\phasetwo removes one edge at a time from the graph \gr (line~\ref{fig:rules:phase2remove}),
checks if the graph remains sufficient for crash consistency (line~\ref{fig:rules:phase2sufficient}),
and if so, recurses to remove more edges.
By greedily removing one edge at a time,
\phasetwo is guaranteed to find a minimal result,
and because \phasetwo considers removing every possible edge from \gr
(except those that cannot lead by solutions by \cref{thm:synthesis:monotonicity}),
it is complete---if an acyclic solution exists, \phasetwo will reach it.\tighten

>>>>

\begin{figure}
    \centering
    {\input{figs/alg.tex}}
    \caption{The \depsynth algorithm takes as input a storage system implementation $\sys$,
    a set of litmus tests \tests, and a crash-consistency predicate $\textrm{\emph{Consistent}}$,
    and returns an acyclic set of dependency rules that make all tests in \tests crash consistent (\cref{def:crash-consistent}).
    The search synthesizes dependency rules for one litmus test at a time.
    If the rules generated for two or more tests result in a cycle,
    this algorithm fails; \cref{sec:alg:cycles} discusses an extension for continuing 
    the search for an acyclic solution.}
    \label{fig:alg:depsynth}
\end{figure}

@@

\begin{figure}
    \centering
    {\input{figs/rules.tex}}
    \caption{The algorithm for generating sufficient dependency rules for a litmus test \test
    searches the space of happens-before graphs over the writes performed by \test.
    The first phase searches for total orders over the writes that are sufficient for crash consistency.
    Once such a total order is found, the second phase (shown in \autoref{fig:alg:phase2}) removes edges
    from it until the happens-before graph is minimal.}
    \label{fig:alg:rulesfortests}
\end{figure}

@@

\begin{figure}
    \centering
    {\input{figs/phase2.tex}}
    \caption{The second phase of the dependency rules generation algorithm. This phase
    greedily removes edges to from the happens-before graph to arrive at a minimal graph.}
    \label{fig:alg:phase2}
\end{figure}

\paragraph{Partial order search.}
Starting from a happens-before graph \gr that reflects a total order over all writes in \test,
\phasetwo (\autoref{fig:alg:phase2})
removes edges from the graph until it is minimal,
i.e., removing any further edges would violate crash consistency.
\phasetwo removes one edge at a time from the graph \gr (line~\ref{fig:rules:phase2remove}),
checks if the graph remains sufficient for crash consistency (line~\ref{fig:rules:phase2sufficient}),
and if so, recurses to remove more edges.
By greedily removing one edge at a time,
\phasetwo is guaranteed to find a minimal result,
and because \phasetwo considers removing every possible edge from \gr
(except those that cannot lead by solutions by \cref{thm:synthesis:monotonicity}),
it is complete---if an acyclic solution exists, \phasetwo will reach it.\tighten

\begin{figure}
    \centering
    {\input{figs/rulesforgraph.tex}}
    \caption{The procedure for generalizing a happens-before graph \gr into dependency rules
    constructs (at most) one rule for each edge.}
    \label{fig:alg:rulesforgraph}
\end{figure}
